Optimal Task Phasing for End-To-End Latency in Harmonic and Semi-Harmonic Automotive Systems

### 2024-09-25 paper.tex
motivating example

	In this section, we demonstrate the impact of task phasing on the end-to-end latency. 
	To that end, we consider an example cause-effect chain $E = (\tau_1 \to \tau_2 \to \tau_3)$ with 
	\begin{itemize}
		\item $\tau_1,\tau_3 \in \mathit{Per}(10)$
		\item $\tau_2 \in \mathit{Per}(1)$.
	\end{itemize}

	The typical approach of making the task set synchronous, i.e., $\tau_1, \tau_2, \tau_3 \in \mathit{Phase}(0)$ leads to the schedule depicted in Figure

	\begin{figure}
		\centering
		\subfloat[Synchronous: $\lat(E) = 40$.]{
		\footnotesize
		\begin{tikzpicture}[yscale=0.22, xscale=0.2]

@@

			\end{scope}
			\end{tikzpicture}	
		}\label{fig:motivation:synchronous}
		\\
		\subfloat[Optimized phasing: $\lat(E) = 31$]{
		\footnotesize
		\begin{tikzpicture}[yscale=0.22, xscale=0.2]

@@

			\end{scope}
			\end{tikzpicture}	
		}\label{fig:motivation:phasing}
		\caption{Motivating example. The longest $1$-partitioned job chain is marked in gray. Changing the phase of task $\tau_3$ from $0$ to $1$ improves the end-to-end latency by $22.5\%$.}
		\label{fig:motivation}
	\end{figure}

	Show that releasing all jobs at the same time is not optimal, and that you can get better results by manipulating phases.

>>>>

	In this section, we demonstrate the impact of task phasing on the end-to-end latency. 
	To that end, we consider an example cause-effect chain $E = (\tau_1 \to \tau_2 \to \tau_3)$ with: 
	\begin{itemize}
		\item $\tau_1,\tau_3 \in \mathit{Per}(10)$
		\item $\tau_2 \in \mathit{Per}(1)$.
	\end{itemize}
	%
	The typical approach of making the task set synchronous, i.e., $\tau_1, \tau_2, \tau_3 \in \mathit{Phase}(0)$ leads to the schedule depicted in Figure~\ref{fig:motivation:synchronous}.
	%
	\begin{figure}
		\centering
		\subfloat[Synchronous: $\lat(E) = 40$.]{
		\footnotesize
		\begin{tikzpicture}[yscale=0.22, xscale=0.2]

@@

			\end{scope}
			\end{tikzpicture}	
		\label{fig:motivation:synchronous}}
		\\
		\subfloat[Optimized phasing: $\lat(E) = 31$]{
		\footnotesize
		\begin{tikzpicture}[yscale=0.22, xscale=0.2]

@@

			\end{scope}
			\end{tikzpicture}	
		\label{fig:motivation:phasing}}
		\caption{Motivating example. The longest $1$-partitioned job chain is marked in gray. Changing the phase of task $\tau_3$ from $0$ to $1$ improves the end-to-end latency by $22.5\%$.}
		\label{fig:motivation}
	\end{figure}
	%
	The longest $1$-partitioned job chain is $\pc^1_1$, marked in gray. 
	Therefore, the end-to-end latency is $\ell(\pc^1_1) = 40$ time units for the synchronous case.

	We observe in Figure~\ref{fig:motivation:synchronous}, that after the write-event of the gray job of $\tau_2$, the next read-event of task $\tau_3$ is time units later. 
	Therefore, by moving the phase of $\tau_3$ from $0$ to $1$, we ensure that the data is read by task $\tau_3$ immediately after it was written by $\tau_2$.
	Specifically, Figure~\ref{fig:motivation:phasing} depicts the case with modified phase $\tau_3 \in \mathit{Phase}(1)$.
	The longest $1$-partitioned job chain has a length of $\ell(\pc^1_1) = 31$.
	Therefore, the end-to-end latency for the case with modified phase is $\lat(E) = 31$.
	We conclude that modifying the phase of $\tau_3$ by only $1$ time unit improved the end-to-end latency by $\frac{9}{40} = 22.5\%$.
